Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-09-30 paper.tex
Updated Proposal
Work in progress.

        \subsubsection{Growth} As in nature, all individuals constantly grow, mature,
        or age. With increasing age, individuals may lose strength but may also gain
        knowledge to solve problems. We represent this with a possible mutation in each
        increment of age.

>>>>

        \subsubsection{Growth} In our algorithm representation, there is a
        direct correlation between elapsed time and the population's evolution.
        For this to be possible in our proposal, all individuals must grow
        older and change as time progresses. With each increment of age, an
        individual may improve or deteriorate. We chose to manifest this idea
        by performing a small mutation in each change.
